Context Segregation
===================
In this set of experiments, we analyse the impact of a new parameter called context tolerance in the convergence to consensus. 
In the previous experiments agents switched between networks using a __*switching probability*__. In the model of *context segregation*, agents switchich using a *segregation criteria* first--**based on a tolerance threshold**--and the same *switching probability* as follows.

At the end of each interaction an agent computes the *ratio of agents with an opposing opinion values* in its current neighbourhood. If this ratio is greater than the *threshold* defined for the current network, the agent switches to a different network immediately; if not, the agent switches using the *switching probability*. 

Load the dependencies for this report.
```{r}
source("../R/experiment_utils.R")

library(data.table)
library(reshape2)
library(ggplot2)
```


# Exploring the Tolerance Threshold Span #
To explore the effect of adding the context threshold to the previous model of context switching, we fixed the **switching probability values in the values {0.25, 0.5, 0.75}** and varied the **context threshold from 0 to 1 in intervals of 0.05**.

## Tolerance Threshold Span for Regular Networks ##
In these experiments we wanted to observe the effect of the context tolerance parameter with scale-free networks. We used *2 networks*. We tested configurations with **switching probability set to 0.25 and 0.75** and **2 k-regular networks with k=5,10,30**. We adjusted the connectivity to observe the effect of the different in the clustering coefficient (and average path length although the difference in clustering coefficient for two networks is more prominent--see [network properties experiment](http://rpubs.com/davidelnunes/socsim_network_properties)).

```{r}
contour_analysis <- function(prop_name,prop_value,cs_values,encounter_data,brks){
  for(cs in cs_values){
    col <- paste("network.0.",prop_name, sep = "")
    current_data <- encounter_data[encounter_data[col] == prop_value & encounter_data$"network.0.cs" == cs,]
    melted_encounters <- melt(current_data,id.vars=c("cfg.id","run","network.0.ct","network.1.ct","network.0.cs",col), measure.vars=c("total-encounters"))
  
    #aggregate encounter data
    agg_encounters <- aggregate(melted_encounters$value,by=list(melted_encounters$network.0.ct,melted_encounters$network.1.ct),mean)
    colnames(agg_encounters) <- c("ct0","ct1","value")
    
    #breaks in the contour
    guide_title <- "Average Encounters"
    net1label <- paste("\n\nTolerance for Network 1 \n Regular Network, ",prop_name,"=",prop_value,sep="") 
    net2label <- paste("\n\nTolerance for Network 2 \n Regular Network, ",prop_name,"=",prop_value,sep="") 
  
    
    encouters_contour <- create_tolerance_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title,xlab=net1label, ylab=net2label)


    print(encouters_contour)
  }
}

```


# Opinion Segregation #
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation/regular_networks/param-space_2014-07-25_19:46:42experiment:20_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```
### Regular Network with K = 5 ###

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(30000,50000,70000,100000,120000,180000))
```

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 10, cs_values = csvalues, encounter_data = encounter_data, brks=c(10000,20000,40000,120000))

```

```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 30, cs_values = csvalues, encounter_data = encounter_data, brks=c(2000,4000,10000,70000))
```

```{r}
#we don't need the persp plots here for now
#reshape the data to display average number of encounters
#encounter_table <- dcast(data=melted_encounters, network.0.ct~network.1.ct, mean)

#average encounters as a matrix
#encounter_matrix <- as.matrix(encounter_table[,-1])
#colnames(encounter_matrix) <- c()

#xlab<- net1label
#ylab<- net2label
#zlab<-"\n\n\n Avg. Encounters"
#plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
```

## Scale-Free Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation/scale-free_networks/param-space_2014-06-30_01:40:06experiment:20_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.d")], by="cfg.id")
head(encounter_data)

```
### D = 1 ###
```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "d",prop_value = 1, cs_values = csvalues, encounter_data = encounter_data, brks=c(104000,110000,120000))
```

### D = 5 ###
```{r}
csvalues <- c(0.25,0.75)
contour_analysis(prop_name = "d",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(3000,5000,10000,20000))
```

# Conformism Segregation #
In this model we did the opposite of segregation from opposite opinions, the agents switch to avoid conformism. If the number of agents
with the same opinion rises above the tolerance threshold the agents switch to another context. 

## K-Regular Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_conformism/regular_networks/param-space_2014-07-23_20:20:09experiment:50_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation_conformism/regular_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.k")], by="cfg.id")
head(encounter_data)
```

### K = 5 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(5000,10000,15000))
```

### K = 10 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 10, cs_values = csvalues, encounter_data = encounter_data, brks=c(5000,10000,15000))
```

### K = 30 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "k",prop_value = 30, cs_values = csvalues, encounter_data = encounter_data, brks=c(1500,1800,2000))
```

## Scale-Free Networks ##
```{r}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_segregation_conformism/scale-free_networks/param-space_2014-07-24_14:56:15experiment:51_.csv")

#read data for number of encounters
encounter_data <- fread("../data/context_segregation_conformism/scale-free_networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.ct","network.1.ct","network.0.cs","network.0.d")], by="cfg.id")
head(encounter_data)

```
### D = 1 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "d",prop_value = 1, cs_values = csvalues, encounter_data = encounter_data, brks=c(20000,40000,50000,70000))
```

### D = 5 ###
```{r}
csvalues <- c(0.25,0.5,0.75)
contour_analysis(prop_name = "d",prop_value = 5, cs_values = csvalues, encounter_data = encounter_data, brks=c(2000,3000))
```

# Analysis with Multiple Networks #
We now look at the influence of multiple network by "freezing" the value of tolerance in an optimal configuration --in terms of speed of convergence. We compare the effects of having multiple networks 
for switching values of **0.25, 0.5 and 0.75**.

```{r}
params <- "../data/context_segregation/multiple-networks/regular-networks/param-space_2014-07-27_18:49:08experiment:20_.csv"

encounters <- "../data/context_segregation/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

##K-regular networks with k = 5##
```{r}
for(cs in c(0.25,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  
  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")


  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)   
   
  
  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))
  
  
   print(plot)
}

```

##Context Switching with Conformism Segregation##
```{r}
params <- "../data/context_segregation_conformism/multiple-networks/regular-networks/param-space_2014-07-27_18:51:59experiment:20_.csv"

encounters <- "../data/context_segregation_conformism/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)


encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

```{r}


for(cs in c(0.25,0.5,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  
  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")


  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)   
   
  
  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))
  
  
   print(plot)
}

```

##Context Switching with Segregation and Selective Switching##
In this model, agents keep a record of how many times they have switched from each network. The **switch to** a particular network based with a probability inversely proportional to the number of times they have switched from that network **using segregation**.

```{r}
params <- "../data/context_segregation_selective/multiple-networks/regular-networks/param-space_2014-07-27_18:58:16experiment:20_.csv"

encounters <- "../data/context_segregation_selective/multiple-networks/regular-networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)


encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
```

```{r}
for(cs in c(0.25,0.5,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]

  
  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")


  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)   
   
  
  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))
  
  
   print(plot)
}

```



